---
title: "Developing Data Products wk 4 Assignment"
author: "Ryan Obuchowski"
date: "1/17/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction 

- This presentation is part of the week four assignment in Developing Data Products on Coursera. It's purpose is to pitch an app that I developed using Shiny in Rstudio to help people understand their yearly savings by taking into account their monthly costs and savings 
- Note: This application takes into account constant monthly income and costs.  Many times, income and costs fluctuate throughout the year. 


## Application

1. This application was named **finances** and can be found here:

https://robuchowski.shinyapps.io/finances/

2. In the application, anyone who is interested in projecting their yearly savings can input their monthly income and costs. 
3. This application allows users to break down their income and costs into distinct categories.
4. For the Income Category, a user can input their monthly income and vested investments
5. For Costs Category, a user can input their monthly Rent, Utilities, Insurance, Car Payments, and Food Costs


## Example R Code

Below is the R code that is performing the calculations for yearly savings, which yields a yearly savings of **$11,100.**

``` {r, echo= TRUE,}
income <- 3000;investments <- 25
monthlyRent <- 800;monthlyUtilities <- 200
monthlyInsurance <- 300; monthlyCar <- 450
monthlyFood <- 350

result <- ((income * 12) + (investments * 12)) + ((-monthlyRent * 12) + (-monthlyUtilities * 12) + (-monthlyInsurance * 12) + (-monthlyCar * 12) + (-monthlyFood *12))
result
```

## Conclusion

This app can be a useful tool for those interested in financially planning their year by performing a quick calculation of their projected yearly savings. The GitHub repository containg the Shiny programs (ui.R and server.R) can be found here:

https://github.com/robuchowski/DataProductsWk4

